MonteCarlo Simulation's of the Covid-19 Pandemic

### 2022-12-14 chien_sim.Rmd

ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases")

ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths")
```

@@

## Day of flex (trial)

```{r}
# trial 1
test <- model_fa[11,]
model_try <- nlsLM(test ~ gauss_fn(days,a,b,c,d), 
                 data=italy_mod, 
                 start=list(a=50000,b=50000,c=.01,d=1))
est_try <- summary(model_try)$parameters
est_try <- est_try[, 1]
names(est_try) <- NULL
# fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}

fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
fn_try_deriv <- D(fn_try_deriv,'x')
x=seq(1,67,length.out=6700)
tmp <- eval(fn_try_deriv)
min(x[tmp < 0])
```

##

@@

```{r}
#plot
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=2, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases") + 
  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1.5, linetype="dashed")

ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=df_italy, color="#1b95ff", size=2, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths") + 
  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1.5, linetype="dashed")
```

>>>>

ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases")

ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths")
```

@@

## Day of flex (test)

```{r}
# test <- model_fa[11,]
# model_try <- nlsLM(test ~ gauss_fn(days,a,b,c,d), 
#                  data=italy_mod, 
#                  start=list(a=50000,b=50000,c=.01,d=1))
# est_try <- summary(model_try)$parameters
# est_try <- est_try[, 1]
# names(est_try) <- NULL
# # fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}
# 
# erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
# 
# fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
# fn_try_deriv <- D(fn_try_deriv,'x')
# x=seq(1,67,length.out=6700)
# tmp <- eval(fn_try_deriv)
# min(x[tmp < 0])
```

## Day of flex

@@

```{r}
#plot
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Cases in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Cases") + 
  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1, linetype="dashed")

ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    labs(title = "Total Deaths in Italy from 2/15/2020 to 3/29/2020 (44 days)", x = "Days", y = "Total Deaths") + 
  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1, linetype="dashed")
```
